A mixture of hidden Markov models to predict the lymphatic spread in head and neck cancer depending on primary tumor location

### 2024-10-22 _tex/manuscript.tex
Built site for gh-pages

For the analyses in this work, we used seven datasets from 5
institutions resulting in 2741 patients in total.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  0 oropharyngeal patients from the University of Zurich in Switzerland
\item
  0 oropharyngeal patients from the Centre Léon Bérard in France
\item
  0 oropharyngeal, larynx and oral cavity patients from the Inselspital
  Bern in Switzerland
\item
  0 oropharyngeal, larynx and oral cavity patients from the Centre Léon
  Bérard in France
\item
  0 oropharyngeal, larynx and oral cavity patients from the University
  of Zurich in Switzerland
\item
  164 oropharyngeal patients from the Hospital Vall d'Hebron in Spain
  (not yet public)
\item
  979 hypopharynx, larynx and oral cavity patients from University
  Medical Center Groningen (not yet public)
\end{enumerate}

The datasets 1-4 are publicly available as CSV tables
\citep{ludwig_multi-centric_2023, ludwig_detailed_2022} and can be
interactively explored on \href{https://lyprox.org}{LyProX}. For each
patient the primary tumor subsite is reportd and each indicidual LNL is
reported as either metastatic or healthy given the available diagnostic
modalities, which include pathology after neck dissection in some
patients. In this work we will stratify the tumor locations into
different ICD codes which are depicted in figure~\ref{fig-subsites}.

>>>>

For the analyses in this work, we used seven datasets from 5
institutions resulting in 2437 patients in total.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  287 oropharyngeal patients from the University of Zurich in
  Switzerland
\item
  263 oropharyngeal patients from the Centre Léon Bérard in France
\item
  327 oropharyngeal, larynx and oral cavity patients from the
  Inselspital Bern in Switzerland
\item
  276 oropharyngeal, larynx and oral cavity patients from the Centre
  Léon Bérard in France
\item
  273 oropharyngeal, larynx and oral cavity patients from the University
  of Zurich in Switzerland
\item
  164 oropharyngeal patients from the Hospital Vall d'Hebron in Spain
  (not yet public)
\item
  847 hypopharynx, larynx and oral cavity patients from University
  Medical Center Groningen (not yet public)
\end{enumerate}

The datasets 1-4 are publicly available as CSV tables
\citep{ludwig_multi-centric_2023, ludwig_detailed_2022} and can be
interactively explored on \href{https://lyprox.org}{LyProX}. For each
patient the primary tumor subsite is reported and each individual LNL is
reported as either metastatic or healthy given the available diagnostic
modalities, which include pathology after neck dissection in some
patients. In this work we will stratify the tumor locations into
different ICD codes which are depicted in figure~\ref{fig-subsites}. For
glottis tumors (C32.0), only t-stages T2,T3 and T4 have been taken into
account as by definition glottis tumors are non-metastatic in the stages
T0 and T1.
